---
title: "Data Cleaning_Part_5"
author: "Sofia Villamil"
date: "2024-06-06"
output: html_document
---

### STARTING WITH INSTAGRAM SCRAPPING

We will attain a variable for the followers that each actor has. However, first to reduce the scrapping amount we will clean the data eliminating the movies with a lot of NA's.

```{r}
rm(list = ls())

```

```{r}
library(readr)
library(writexl)
library(dplyr)
library(tidyr)
library(openxlsx)

```

```{r}
data <- read_csv("C:/Users/sofia/Documents/Documentos/Master Computational Social Sciences/TFM/Master Thesis/Scrapping and Data Part 2/data_final_3.csv", show_col_types = FALSE)

```

### First we look for duplicates.

```{r}
# Identify duplicated titles
duplicates <- data[duplicated(data$imdb_id) | duplicated(data$imdb_id, fromLast = TRUE), ]
data <- data[!duplicated(data$imdb_id), ]
```

### Now we look at the Na's

```{r}
data_filtered <- data[ , !(names(data) %in% c("FirstWriter_imdb", "production_countries"))]

```

```{r}
data_filtered <- data_filtered[!is.na(data_filtered$"IMDbscore_imdb"), ]
data_filtered <- data_filtered[!is.na(data_filtered$"Duration_mov_imdb"), ]
data_filtered <- data_filtered[!is.na(data_filtered$"production_companies"), ]
```

```{r}
# Define the columns to check for NA values
columns_to_check_1 <- c("FeatureReview_imdb", 
                      "top_critic_review_1_rt", "top_critic_review_2_rt", 
                      "audience_review_1_rt", "audience_review_2_rt")

# Remove rows where all specified columns are NA
data_filtered_2 <- data_filtered[rowSums(is.na(data_filtered[, columns_to_check_1])) != length(columns_to_check_1), ]

```

```{r}
columns_to_check_2 <- c("critics_score_rt", "audience_score_rt")

data_filtered_3 <- data_filtered_2[rowSums(is.na(data_filtered_2[, columns_to_check_2])) != length(columns_to_check_2), ]
```

```{r}
na_counts <- colSums(is.na(data_filtered_3))
na_counts
```

### Changes

```{r}
# Filling one observation that was missing
data_filtered_3[data_filtered_3$imdb_id == "tt6449410", "Genre_imdb"] <- "Comedy" # found it in rotten tomatoes as in imdb there was no info
```

```{r}
# there are movies who do not have actors as they are animated or documentaries. So the director is going to be the actor.

na_condition <- is.na(data_filtered_3$FirstActor_imdb) & is.na(data_filtered_3$SecondActor_imdb)

# Fill FirstActor_imdb and SecondActor_imdb with Director_imdb if both are NA
data_filtered_3$FirstActor_imdb[na_condition] <- data_filtered_3$Director_imdb[na_condition]
data_filtered_3$SecondActor_imdb[na_condition] <- data_filtered_3$Director_imdb[na_condition]

# Some movies have only one actor
data_filtered_3$SecondActor_imdb[is.na(data_filtered_3$SecondActor_imdb)] <- "None"

```

```{r}
# Now for the MPAA, some are not rated.
# Replace NA values with "Not Rated"
data_filtered_3$MPAA_imdb[is.na(data_filtered_3$MPAA_imdb)] <- "Not Rated"

# Replace "Unrated" values with "Not Rated"
data_filtered_3$MPAA_imdb[data_filtered_3$MPAA_imdb == "Unrated"] <- "Not Rated"
```

```{r}
#write.csv(data_filtered_3, "C:/Users/sofia/Documents/Documentos/Master Computational Social Sciences/TFM/Master Thesis/Scrapping and Data Part 2/data_final_4.csv",row.names = FALSE)

```

After this script we will now go to the last scrapping script called "Scrapping TMDB selected movies_Part_6".
