---
title: "Scrapping for Budget using The Numbers"
author: "Sofia Villamil"
date: "2024-06-10"
output: html_document
---

### SCRAPPING THE NUMBERS

We need to get the budget to have a clear variable able to indentify if a movie was successful or not. This is why we are going to scrap the budget information for the Numbers (Link: <https://www.the-numbers.com/>).

```{r}
rm(list = ls())
```

#### Library

```{r}
library(readr)
library(lubridate) # for release data
library(tidyverse)
library(rvest)
library(httr)
library(dplyr)
library(foreach)
library(doParallel)
```

```{r}
set_config(user_agent("Mozilla/5.0 (Windows NT 10.0; Win64; x64) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/121.0.0.0 Safari/537.36; Sofia Villamil / sofia.v1999@gmail.com")) # set your user agent here
```

```{r}
data <- read_csv("data_final.csv", show_col_types = FALSE)

```

I need the year for the scrapping

```{r}
data <- data %>%
  mutate(release_date = dmy(release_date))%>%
  mutate(release_year = year(release_date))
```

#### Titles with Na's in their Budget

```{r}
na_titles <- data %>% 
  filter(is.na(Budget)) %>% 
  select(title,imdb_id,release_year)
```

```{r}
na_titles <- na_titles[1:10,]
```

```{r}
na_titles$release_year_numbers <- na_titles$release_year - 1
```

#### Gathering the data

There are four specific variations in the URLs structure that I will take into account.

```{r}
# Function to create the URL with release year in brackets
create_movie_url_with_year <- function(title, release_year_numbers) {
  base_url <- "https://www.the-numbers.com/movie/"
  formatted_title <- gsub("[^A-Za-z0-9]", "-", title)
  url <- paste0(base_url, formatted_title, "-(", release_year_numbers, ")#tab=summary")
  return(url)
}

# Function to create the URL with "The" moved to the end
move_the_to_end <- function(title) {
  if (startsWith(title, "The ")) {
    title <- sub("^The (.+)", "\\1-The", title)
  }
  return(title)
}

create_movie_url_with_the <- function(title) {
  base_url <- "https://www.the-numbers.com/movie/"
  formatted_title <- gsub("[^A-Za-z0-9]", "-", move_the_to_end(title))
  url <- paste0(base_url, formatted_title, "#tab=summary")
  return(url)
}

# Function to create the basic URL without any modifications
create_movie_url_basic <- function(title) {
  base_url <- "https://www.the-numbers.com/movie/"
  formatted_title <- gsub("[^A-Za-z0-9]", "-", title)
  url <- paste0(base_url, formatted_title, "#tab=summary")
  return(url)
}

```

Scrapping Function

```{r}
scrape_budget_from_url <- function(url) {
  print(paste("Scraping URL:", url)) 
  webpage <- tryCatch({
    read_html(url)
  }, error = function(e) {
    message(paste("Failed to read URL:", url))
    return(NULL)
  })
  
  if (is.null(webpage)) {
    return(NA)
  }

  budget <- tryCatch({
    result <- webpage %>%
      html_nodes(xpath = "//tr[td/b[contains(text(),'Production')]]/td[2]") %>%
      html_text() %>%
      str_extract("\\$[\\d,]+") %>%
      gsub("[\\$,]", "", .) %>%
      as.numeric()
    if(length(result) > 0) result[1] else NA
  }, error = function(e) {
    message(paste("Failed to extract budget from URL:", url))
    return(NA)
  })

  if (is.na(budget)) {
    message(paste("Budget not found in URL:", url))
  }
  
  return(budget)
}

# Function to scrape budget using the different URLs
scrape_budget <- function(title, year) {
  urls <- c(
    create_movie_url_with_year(title, year),
    create_movie_url_with_the(title),
    create_movie_url_basic(title),
    create_movie_url_with_year(title, year - 1)  
  )
  
  for (url in urls) {
    budget <- scrape_budget_from_url(url)
    if (!is.na(budget)) {
      return(budget)
    }
  }
  return(NA)
}

# parallel processing
num_cores <- detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)

results <- foreach(i = 1:nrow(na_titles), .combine = rbind, .packages = c('rvest', 'stringr', 'dplyr')) %dopar% {
  title <- na_titles$title[i]
  imdb_id <- na_titles$imdb_id[i]
  release_year <- na_titles$release_year[i]
  budget <- scrape_budget(title, release_year)
  Sys.sleep(1)  
  data.frame(title = title, imdb_id = imdb_id, release_year = release_year, Budget = budget, stringsAsFactors = FALSE)
}

stopCluster(cl)

```


```{r}
#write.csv(results, "C:/Users/sofia/Documents/Documentos/Master Computational Social Sciences/TFM/Master Thesis/Scrapping and Data Part 2/scrapping_url_1.csv",row.names = FALSE)

```

#### Joining the data set and saving

```{r}
merged_data <- data %>%
  left_join(results, by = "imdb_id", suffix = c("", "_scraped")) %>%
  mutate(Budget = ifelse(is.na(Budget), Budget_scraped, Budget)) %>%
  select(-Budget_scraped,-title_scraped, - release_year_scraped,-release_year)
```

```{r}
#write.csv(merged_data, "C:/Users/sofia/Documents/Documentos/Master Computational Social Sciences/TFM/Master Thesis/Scrapping and Data Part 2/data_final_3.csv",row.names = FALSE)

```
We are going now to continue with the script "Data Cleaning_Part_5"
