---
title: "Extra Model with social media_Part_3"
author: "Sofia Villamil"
date: "2024-06-15"
output: html_document
---
 ## Support Vector Machine Model
 
This will be the variables we are going to add to our model.We are going to repeat the process again

-   View Count in Trailer: Numeric normalized variable created with the number of view the trailer for each movie has on Youtube.

-   First Actor and Second Actor Instagram Followers: Numeric normalized variable created with the total amount of followers each actor has on Instagram.

Due to the limits and time obtaining the data for the followers of each actor the data set is really small, this is why we are going to use a SVM model as it able to deal better with smaller data set.

```{r}
rm(list = ls())
```

#### Library
```{r}
library(readr)
library(e1071)
library(readxl)
library(dplyr)
library(lubridate)
library(stringr)
library(tidyr)
library(doParallel)
library(future)
library(sentimentr)
library(future.apply)
library(purrr)
library(ggplot2)
library(extrafont)
#font_import()
#loadfonts(device = "win")
library(pdp)
library(ggplot2)
```

### Creating the variables for this small data set

```{r}
data_final_5 <- read_csv("C:/Users/sofia/Documents/Documentos/Master Computational Social Sciences/TFM/Master Thesis/Scrapping and Data Part 2/data_final_5.csv", show_col_types = FALSE)
```

### Youtube Variable
```{r}
results_youtube_1 <- read_delim("C:/Users/sofia/Documents/Documentos/Master Computational Social Sciences/TFM/Master Thesis/Modeling Part 3/Youtube and Instagram Data/results_youtube_1.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE,show_col_types = FALSE)
results_youtube_1 <- results_youtube_1[, -3]

```

```{r}
# Function to convert view counts to numeric values
convert_view_count <- function(view_count) {
  if (grepl("B", view_count, ignore.case = TRUE)) {
    return(as.numeric(gsub("[^0-9.]", "", view_count)) * 1e9)
  } else if (grepl("M", view_count, ignore.case = TRUE)) {
    return(as.numeric(gsub("[^0-9.]", "", view_count)) * 1e6)
  } else if (grepl("K", view_count, ignore.case = TRUE)) {
    return(as.numeric(gsub("[^0-9.]", "", view_count)) * 1e3)
  } else {
    return(as.numeric(gsub("[^0-9.]", "", view_count)))
  }
}

# Apply the conversion function
results_youtube_1$view_count <- sapply(results_youtube_1$view_count, convert_view_count)

```

```{r}
# Ensure the view_count column is numeric
results_youtube_1$view_count <- as.numeric(results_youtube_1$view_count)

# Function to normalize data using Min-Max normalization
normalize_min_max <- function(x) {
  return((x - min(x, na.rm = TRUE)) / (max(x, na.rm = TRUE) - min(x, na.rm = TRUE)))
}

# Apply normalization to the view_count column
results_youtube_1$view_count_normalized <- normalize_min_max(results_youtube_1$view_count)

```

```{r}
data_final_5 <- merge(data_final_5, results_youtube_1, by = "title", all.x = TRUE)
```

### Instagram Variable

```{r}
results_instagram_1 <- read_excel("C:/Users/sofia/Documents/Documentos/Master Computational Social Sciences/TFM/Master Thesis/Modeling Part 3/Youtube and Instagram Data/results_instagram_1.xlsx")
results_instagram_1$Instagram_followers <-results_instagram_1$`Instagram Followers`
results_instagram_1 <- results_instagram_1[, -2]

```

```{r}
# Function to convert view counts to numeric values
convert_followers <- function(Instagram_followers) {
  if (grepl("B", Instagram_followers, ignore.case = TRUE)) {
    return(as.numeric(gsub("[^0-9.]", "", Instagram_followers)) * 1e9)
  } else if (grepl("M", Instagram_followers, ignore.case = TRUE)) {
    return(as.numeric(gsub("[^0-9.]", "", Instagram_followers)) * 1e6)
  } else if (grepl("K", Instagram_followers, ignore.case = TRUE)) {
    return(as.numeric(gsub("[^0-9.]", "", Instagram_followers)) * 1e3)
  } else {
    return(as.numeric(gsub("[^0-9.]", "", Instagram_followers)))
  }
}

# Apply the conversion function
results_instagram_1$Instagram_followers <- sapply(results_instagram_1$Instagram_followers, convert_followers)

results_instagram_1$Instagram_followers[is.na(results_instagram_1$Instagram_followers)] <- 0


# Filter out rows with less than 10,000 followers because they are fan pages.

results_instagram_1$Instagram_followers[results_instagram_1$Instagram_followers < 10000] <- 0

```


```{r}
# Merge normalized_actor_score for First Actor
data_final_5 <- data_final_5 %>%
  left_join(results_instagram_1, by = c("FirstActor_imdb" = "name")) %>%
  rename(FirstActor_followers = Instagram_followers)

# Merge normalized_actor_score for Second Actor
data_final_5 <- data_final_5 %>%
  left_join(results_instagram_1, by = c("SecondActor_imdb" = "name")) %>%
  rename(SecondActor_followers = Instagram_followers)
```


## Other variables
```{r}
na_count <- sum(is.na(data_final_5$FirstActor_followers))
na_count
```

```{r}
na_count <- sum(is.na(data_final_5$SecondActor_followers))
na_count
```


```{r}
data_final_5 <- data_final_5 %>%
  filter(!is.na(SecondActor_followers))

data_final_5 <- data_final_5 %>%
  filter(!is.na(FirstActor_followers))

data_final_5 <- data_final_5 %>%
  filter(!is.na(view_count))

```

```{r}
data_final_5 <- data_final_5 %>%
  filter(!is.na(Budget))
```

### Genre

```{r}
unique_genres <- data_final_5 %>%
  group_by(Genre_imdb) %>%
  summarise(count = n()) %>%
  ungroup()
unique_genres
```

Creating the genre dummy for analysis, it will take the value one if the movie is a certain genre.

```{r}
# Ensure Genre is a factor
data_final_5 <- data_final_5 %>%
  mutate(Genre_imdb = factor(Genre_imdb))

# crating the dummy variables
dummy <- dummyVars(" ~ Genre_imdb", data = data_final_5)
data_final_encoded <- as.data.frame(predict(dummy, newdata = data_final_5))

```

```{r}
# combining the columns
data_final_5 <- bind_cols(data_final_5, data_final_encoded)

data_final_5 <- data_final_5 %>%
  select(-Genre_imdb)
```

### MPAA

```{r}
unique_MPAA <- data_final_5 %>%
  group_by(MPAA_imdb) %>%
  summarise(count = n()) %>%
  ungroup()
unique_MPAA
```

There are 36 distinct ratings, we will standardize it for the analysis using the Motion Pictures Association Rating Guide (Click here for the interactive guide: <https://www.motionpictures.org/film-ratings/>).

```{r}
# Function to standardize ratings
standardize_rating <- function(rating) {
  case_when(
    rating %in% c("G", "TV-Y", "TV-G", "A", "AL", "TP", "A/fig", "A/i", "A/i/fig", "0+", "3", "4", "6+", "TV-Y7") ~ "General Audiences",
    rating %in% c("PG", "TV-PG", "2", "5", "7","7/i","7/fig","10", "12", "12/fig", "13", "13+") ~ "Parental Guidance Suggested",
    rating %in% c("PG-13", "TV-14", "14", "16", "16+", "16/fig", "9+", "M") ~ "Parents Strongly Cautioned",
    rating %in% c("R", "TV-MA", "18", "18+", "18/fig", "NC-17", "X") ~ "Restricted",
    rating %in% c("NC-17") ~ "No One 17 and Under Admitted",
    rating %in% c("Not Rated") ~ "Not Rated",
    TRUE ~ "Unknown"
  )
}

# Apply the function to standardize ratings
data_final_5 <- data_final_5 %>%
  mutate(MPAA = standardize_rating(MPAA_imdb))

# transforming it as a factor
data_final_5 <- data_final_5 %>%
  mutate(MPAA = factor(MPAA))
```

```{r}
# Creating the dummy variable
dummy_mpaa <- dummyVars(" ~ MPAA", data = data_final_5)
data_final_encoded_mpaa <- as.data.frame(predict(dummy_mpaa, newdata = data_final_5))

data_final_5 <- bind_cols(data_final_5, data_final_encoded_mpaa)

data_final_5 <- data_final_5 %>%
  select(-MPAA_imdb, -MPAA)
```

### Original Language

```{r}
data_final_5 <- data_final_5 %>%
  select(-original_language)
```
There are to little observations for each language some even have none observations.

### Duration of the movie

```{r}
# Normalize the duration variable between 0 and 1
data_final_5 <- data_final_5 %>%
  mutate(duration_normalized = (Duration_mov_imdb- min(Duration_mov_imdb)) / (max(Duration_mov_imdb) - min(Duration_mov_imdb)))

summary(data_final_5$duration_normalized)
data_final_5 <- data_final_5 %>%
  select(-Duration_mov_imdb)
```

### Release Date

```{r}
data_final_5 <- data_final_5 %>%
  mutate(release_date = dmy(release_date))
```

```{r}
# Extract year, month, and day
data_final_5 <- data_final_5 %>%
  mutate(release_year = year(release_date),
         release_month = month(release_date),
         release_day = day(release_date))

# Calculate the age of the movie
current_year <- year(Sys.Date())
data_final_5 <- data_final_5 %>%
  mutate(movie_age = current_year - release_year)

# Create a feature to determine if the release date is a weekend
data_final_5 <- data_final_5 %>%
  mutate(is_weekend = if_else(wday(release_date) %in% c(1, 7), 1, 0))

```

Season

```{r}
data_final_5 <- data_final_5 %>%
  mutate(season = case_when(
    month(release_date) %in% c(12, 1, 2) ~ "Winter",
    month(release_date) %in% c(3, 4, 5) ~ "Spring",
    month(release_date) %in% c(6, 7, 8) ~ "Summer",
    month(release_date) %in% c(9, 10, 11) ~ "Fall"
  ))

```

```{r}
# Creating a dummy variable
data_final_5 <- data_final_5 %>%
  mutate(season_ = factor(season))

dummy_season <- dummyVars(" ~ season", data = data_final_5)
data_final_encoded_season <- as.data.frame(predict(dummy_season, newdata = data_final_5))

data_final_5 <- bind_cols(data_final_5, data_final_encoded_season)

data_final_5 <- data_final_5 %>%
  select(-release_date, -season_)
```

### Production Companies

```{r}
data_final_5 <- data_final_5 %>%
  select(-production_companies)
```

### Score

We are going to create a combined score, using the three scores attained and the total voting for those score.

```{r}
# First we normalize IMDb scores to a 0-100 scale equal to the rt one.
data_final_5 <- data_final_5 %>%
  mutate(imdb_score_normalized = IMDbscore_imdb * 10)
```


```{r}
data_final_5 <- data_final_5 %>%
  rowwise() %>%
  mutate(
    # cases with all scores
    weighted_sum_all = sum(
      na.omit(c(imdb_score_normalized,
                critics_score_rt * total_critics_reviews_rt,
                audience_score_rt * total_audience_reviews_rt))),
    total_reviews_all = sum(
      na.omit(c(1, total_critics_reviews_rt, total_audience_reviews_rt))),
    combined_score_all = ifelse(total_reviews_all > 0, weighted_sum_all / total_reviews_all, NA),
    
    # cases missing audience scores
    weighted_sum_no_audience = sum(
      na.omit(c(imdb_score_normalized,
                critics_score_rt * total_critics_reviews_rt))),
    total_reviews_no_audience = sum(
      na.omit(c(1, total_critics_reviews_rt))),
    combined_score_no_audience = ifelse(total_reviews_no_audience > 0, weighted_sum_no_audience / total_reviews_no_audience, NA),
    
    # cases missing critics' scores
    weighted_sum_no_critics = sum(
      na.omit(c(imdb_score_normalized,
                audience_score_rt * total_audience_reviews_rt))),
    total_reviews_no_critics = sum(
      na.omit(c(1, total_audience_reviews_rt))),
    combined_score_no_critics = ifelse(total_reviews_no_critics > 0, weighted_sum_no_critics / total_reviews_no_critics, NA),
    
    # cases with only IMDb scores
    combined_score_imdb_only = imdb_score_normalized,
    
    # combined score creation
    combined_score = case_when(
      !is.na(combined_score_all) ~ combined_score_all,
      !is.na(combined_score_no_audience) ~ combined_score_no_audience,
      !is.na(combined_score_no_critics) ~ combined_score_no_critics,
      TRUE ~ combined_score_imdb_only
    )
  ) %>%
  ungroup()
```

```{r}
data_final_5 <- data_final_5 %>%
  mutate(
    min_combined_score = min(combined_score, na.rm = TRUE),
    max_combined_score = max(combined_score, na.rm = TRUE),
    movie_score = (combined_score - min_combined_score) / (max_combined_score - min_combined_score)
  )
```

```{r}
data_final_5 <- data_final_5 %>%
  select(-min_combined_score, -max_combined_score, -IMDbscore_imdb, -imdb_score_normalized,
         -weighted_sum_all, -total_reviews_all, -combined_score_all,
         -weighted_sum_no_audience, -total_reviews_no_audience, -combined_score_no_audience,
         -weighted_sum_no_critics, -total_reviews_no_critics, -combined_score_no_critics,
         -combined_score_imdb_only, -combined_score)

```

### Director

Let's start with cleaning the variable for the Oscars.

```{r}
oscar_summary <- data_final_5 %>%
  filter(Oscar_Information_imdb != 'Awards') %>%
  group_by(Oscar_Information_imdb) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

```

The top awards will be given waits based on this list (Link:<https://www.therichest.com/luxury/top-10-most-prestigious-movie-awards-in-the-world/>)

```{r}
award_weights <- c(
  'Won 1 Oscar' = 50,
  'Won 2 Oscars' = 100,
  'Won 3 Oscars' = 150,
  'Won 4 Oscars' = 200,
  'Won 5 Oscars' = 250,
  'Won 6 Oscars' = 300,
  'Won 7 Oscars' = 350,
  'Won 1 BAFTA Award' = 30,
  'Won 2 BAFTA Awards' = 60,
  'Won 1 Primetime Emmy' = 20,
  'Won 2 Primetime Emmys' = 40,
  'Nominated for 1 Oscar' = 15,
  'Nominated for 2 Oscars' = 30,
  'Nominated for 3 Oscars' = 45,
  'Nominated for 4 Oscars' = 60,
  'Nominated for 5 Oscars' = 75,
  'Nominated for 1 BAFTA Award' = 10,
  'Nominated for 2 BAFTA Awards' = 20,
  'Nominated for 3 BAFTA Awards' = 30,
  'Nominated for 1 Primetime Emmy' = 5,
  'Nominated for 2 Primetime Emmys' = 10,
  'Nominated for 3 Primetime Emmys' = 15
)

```

```{r}
data_final_5 <- data_final_5 %>%
  mutate(Oscar_Information_imdb = ifelse(Oscar_Information_imdb == "Awards", "No Major Awards", Oscar_Information_imdb))

```

Taking into account that I will also get the number of awards and nominations.

Now we will clean the Awards and nomination variables

```{r}
unique_awards_nominations <- data_final_5 %>%
  select(AwardsAndNominations_imdb) %>%
  distinct() %>%
  arrange(AwardsAndNominations_imdb)
```

Cleaning the column as the movies with no awards need to be cleaned to represent that.

```{r}
data_final_5 <- data_final_5 %>%
  mutate(
    AwardsAndNominations_imdb = ifelse(str_detect(AwardsAndNominations_imdb, "win|wins|nomination|nominations"), 
                                       AwardsAndNominations_imdb, 
                                       "No Awards")
  )

```

```{r}
# Extract wins and nominations
data_final_5 <- data_final_5 %>%
  mutate(
    wins = ifelse(AwardsAndNominations_imdb != "No Awards", 
                  as.numeric(str_extract(AwardsAndNominations_imdb, "\\d+(?=\\s+win|\\s+wins)")), 0),
    nominations = ifelse(AwardsAndNominations_imdb != "No Awards", 
                         as.numeric(str_extract(AwardsAndNominations_imdb, "\\d+(?=\\s+nomination|\\s+nominations)")), 0)
  ) %>% 
  replace_na(list(wins = 0, nominations = 0))

```

```{r}
# Calculate the award score for each director based on their awards and nominations history in my data set
data_final_5 <- data_final_5 %>%
  rowwise() %>%
  mutate(award_score = ifelse(Oscar_Information_imdb %in% names(award_weights), award_weights[Oscar_Information_imdb], 0)) %>%
  ungroup()

# Calculate the number of movies each director has directed in the data set
director_movie_count <- data_final_5 %>%
  group_by(Director_imdb) %>%
  summarise(movie_count = n())

# Calculate the total award score for each director in the data set
director_award_score <- data_final_5 %>%
  group_by(Director_imdb) %>%
  summarise(total_award_score = sum(award_score))

# Aggregate wins and nominations for each director for movies in the data set
director_awards_nominations <- data_final_5 %>%
  group_by(Director_imdb) %>%
  summarise(
    total_wins = sum(wins, na.rm = TRUE),
    total_nominations = sum(nominations, na.rm = TRUE)
  )

director_metrics <- director_movie_count %>%
  left_join(director_award_score, by = "Director_imdb") %>%
  left_join(director_awards_nominations, by = "Director_imdb")

# Normalize wins and nominations to ensure that many small awards don't overshadow big ones. I want the important awards to still have weight.
director_metrics <- director_metrics %>%
  mutate(
    normalized_wins = total_wins / max(total_wins, na.rm = TRUE),
    normalized_nominations = total_nominations / max(total_nominations, na.rm = TRUE)
  )

# combined director score
director_metrics <- director_metrics %>%
  mutate(
    combined_director_score = movie_count + total_award_score + normalized_wins * 10 + normalized_nominations * 5
  )

# Normalize the combined director score 
director_metrics <- director_metrics %>%
  mutate(
    min_score = min(combined_director_score, na.rm = TRUE),
    max_score = max(combined_director_score, na.rm = TRUE),
    normalized_director_score = (combined_director_score - min_score) / (max_score - min_score)
  ) %>%
  select(-min_score, -max_score)


data_final_5 <- data_final_5 %>%
  left_join(director_metrics, by = "Director_imdb")


```

```{r}
columns_to_remove <- c("wins", "nominations", "award_score", "movie_count", "total_award_score", 
                       "total_wins", "total_nominations", "normalized_wins", "normalized_nominations", 
                       "combined_director_score", "Oscar_Information_imdb", "AwardsAndNominations_imdb")

data_final_5 <- data_final_5 %>%
  select(-all_of(columns_to_remove))
```


### Actor

```{r message=FALSE}
actors_info <- read_delim("C:/Users/sofia/Documents/Documentos/Master Computational Social Sciences/TFM/Master Thesis/Modeling Part 3/actors_with_imdb.csv", 
    delim = ",", escape_double = FALSE, trim_ws = TRUE)
```

```{r}
# Merge Instagram followers for First Actor
actors_info <- actors_info %>%
  left_join(data_final_5 %>% select(FirstActor_imdb, FirstActor_followers) %>% rename(Instagram_followers = FirstActor_followers), 
            by = c("name" = "FirstActor_imdb"))

# Merge Instagram followers for Second Actor
actors_info <- actors_info %>%
  left_join(data_final_5 %>% select(SecondActor_imdb, SecondActor_followers) %>% rename(Instagram_followers = SecondActor_followers), 
            by = c("name" = "SecondActor_imdb"))

# Combine the Instagram followers columns
actors_info <- actors_info %>%
  mutate(
    Instagram_followers = coalesce(Instagram_followers.x, Instagram_followers.y)
  ) %>%
  select(-Instagram_followers.x, -Instagram_followers.y)
```

Let's start with cleaning the variable for the Oscars.

```{r}
oscar_summary <- actors_info %>%
  filter(oscars_nominations != 'Awards') %>%
  group_by(oscars_nominations) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

```

The top awards will be given waits based on this list (Link:<https://www.therichest.com/luxury/top-10-most-prestigious-movie-awards-in-the-world/>)

```{r}
award_weights <- c(
  'Won 1 Oscar' = 50,
  'Won 2 Oscars' = 100,
  'Won 3 Oscars' = 150,
  'Won 4 Oscars' = 200,
  'Won 5 Oscars' = 250,
  'Won 6 Oscars' = 300,
  'Won 1 BAFTA Award' = 30,
  'Won 2 BAFTA Awards' = 60,
  'Won 3 BAFTA Awards' = 90,  # New
  'Won 1 Primetime Emmy' = 20,
  'Won 2 Primetime Emmys' = 40,
  'Won 3 Primetime Emmys' = 60,  # New
  'Won 4 Primetime Emmys' = 80,  # New
  'Won 5 Primetime Emmys' = 100,  # New
  'Won 6 Primetime Emmys' = 120,  # New
  'Won 7 Primetime Emmys' = 140,  # New
  'Won 9 Primetime Emmys' = 180,  # New
  'Won 11 Primetime Emmys' = 220,  # New
  'Won 12 Primetime Emmys' = 240,  # New
  'Nominated for 1 Oscar' = 15,
  'Nominated for 2 Oscars' = 30,
  'Nominated for 3 Oscars' = 45,
  'Nominated for 4 Oscars' = 60,
  'Nominated for 5 Oscars' = 75,
  'Nominated for 6 Oscars' = 90,  # New
  'Nominated for 8 Oscars' = 120,  # New
  'Nominated for 12 Oscars' = 180,  # New
  'Nominated for 1 BAFTA Award' = 10,
  'Nominated for 2 BAFTA Awards' = 20,
  'Nominated for 3 BAFTA Awards' = 30,
  'Nominated for 4 BAFTA Awards' = 40,  # New
  'Nominated for 8 BAFTA Awards' = 80,  # New
  'Nominated for 1 Primetime Emmy' = 5,
  'Nominated for 2 Primetime Emmys' = 10,
  'Nominated for 3 Primetime Emmys' = 15,
  'Nominated for 4 Primetime Emmys' = 20,  # New
  'Nominated for 5 Primetime Emmys' = 25,  # New
  'Nominated for 6 Primetime Emmys' = 30,  # New
  'Nominated for 7 Primetime Emmys' = 35,  # New
  'Nominated for 8 Primetime Emmys' = 40,  # New
  'Nominated for 9 Primetime Emmys' = 45,  # New
  'Nominated for 10 Primetime Emmys' = 50,  # New
  'Nominated for 13 Primetime Emmys' = 65  # New
)

```

```{r}
actors_info <- actors_info %>%
  mutate(oscars_nominations = ifelse(oscars_nominations == "Awards", "No Major Awards", oscars_nominations))

```

Now we will clean the Awards and nomination variables

```{r}
unique_awards_nominations2 <- actors_info %>%
  select(awards_and_nominations) %>%
  distinct() %>%
  arrange(awards_and_nominations)
```

Cleaning the column as the movies with no awards need to be cleaned to represent that.

```{r}
actors_info <- actors_info %>%
  mutate(
    awards_and_nominations = ifelse(str_detect(awards_and_nominations, "win|wins|nomination|nominations"), 
                                       awards_and_nominations, 
                                       "No Awards")
  )

```

```{r}
actors_info <- actors_info %>%
  mutate(
    wins = ifelse(awards_and_nominations != "No Awards", 
                  as.numeric(str_extract(awards_and_nominations, "\\d+(?=\\s+win|\\s+wins)")), 0),
    nominations = ifelse(awards_and_nominations != "No Awards", 
                         as.numeric(str_extract(awards_and_nominations, "\\d+(?=\\s+nomination|\\s+nominations)")), 0)
  ) %>% 
  replace_na(list(wins = 0, nominations = 0))

```

For the number of movies, we need to deal first with any Na's found in that variable

```{r}
# Identify actors with NA in number_of_movies
na_actors <- actors_info %>%
  filter(is.na(number_of_movies)) %>%
  pull(name)

# Count their appearances in data_final to fill this Na's with that
actor_appearances <- data_final_5 %>%
  mutate(
    FirstActor_imdb = ifelse(FirstActor_imdb %in% na_actors, FirstActor_imdb, NA),
    SecondActor_imdb = ifelse(SecondActor_imdb %in% na_actors, SecondActor_imdb, NA)
  ) %>%
  pivot_longer(cols = c(FirstActor_imdb, SecondActor_imdb), values_drop_na = TRUE) %>%
  group_by(value) %>%
  summarize(appearances = n())

```

So they each appear 1 time in our data set and in IMDb they also have only 1 previous movie so we are going to set the Na's to 1.

```{r}
actors_info <- actors_info %>%
  mutate(number_of_movies = replace_na(number_of_movies, 1))
```

Following the same calculations we did with director but adding instagram followers

```{r}
actors_info <- actors_info %>%
  filter(!is.na(Instagram_followers))

```

```{r}
actors_info <- actors_info %>%
  rowwise() %>%
  mutate(award_score = ifelse(awards_and_nominations %in% names(award_weights), award_weights[awards_and_nominations], 0)) %>%
  ungroup()

actor_award_score <- actors_info %>%
  group_by(actor_id_imdb) %>%
  summarise(total_award_score = sum(award_score))

actor_awards_nominations <- actors_info %>%
  group_by(actor_id_imdb) %>%
  summarise(
    total_wins = sum(wins, na.rm = TRUE),
    total_nominations = sum(nominations, na.rm = TRUE)
  )

# Combine the metrics with Instagram Followers now.
actor_metrics <- actors_info %>%
  select(actor_id_imdb, number_of_movies, Instagram_followers) %>% 
  distinct() %>%
  left_join(actor_award_score, by = "actor_id_imdb") %>%
  left_join(actor_awards_nominations, by = "actor_id_imdb")


actor_metrics <- actor_metrics %>%
  mutate(
    normalized_wins = total_wins / max(total_wins, na.rm = TRUE),
    normalized_nominations = total_nominations / max(total_nominations, na.rm = TRUE),
    normalized_instagram_followers = Instagram_followers )

# combined actor score
actor_metrics <- actor_metrics %>%
  mutate(
    combined_actor_score = number_of_movies + total_award_score + normalized_wins * 10 + normalized_nominations * 5 + normalized_instagram_followers * 10
  )

```

```{r}
actors_info <- actors_info %>%
  left_join(actor_metrics %>% select(actor_id_imdb, combined_actor_score), by = "actor_id_imdb")
```

```{r}
actors <- actors_info %>%
  select(actor_id_imdb, name, combined_actor_score)
```

```{r}
actors <- actors %>%
  distinct(actor_id_imdb, .keep_all = TRUE)

```

```{r}
# Merge combined_actor_score for First Actor
data_final_5 <- data_final_5 %>%
  left_join(actors, by = c("FirstActor_imdb" = "name")) %>%
  rename(FirstActor_score = combined_actor_score)

# Merge combined_actor_score for Second Actor
data_final_5 <- data_final_5 %>%
  left_join(actors, by = c("SecondActor_imdb" = "name")) %>%
  rename(SecondActor_score = combined_actor_score)
```

```{r}
colnames(data_final_5)
```

### Sentiment Analysis of Reviews

Let´s start with the Reviews Variable.

-   TitleReview_imdb

-   FeatureReview_imdb

-   top_critic_review_1_rt

-   top_critic_review_2_rt

-   audience_review_1_rt

-   audience_review_2_rt

```{r}
data <- data_final_5 %>%
  select(imdb_id, TitleReview_imdb, FeatureReview_imdb, top_critic_review_1_rt, top_critic_review_2_rt, audience_review_1_rt, audience_review_2_rt)

```

```{r}
# Function to calculate sentiment score using sentimentr
get_sentiment <- function(text) {
  if (is.na(text) || length(text) == 0 || text == "") {
    return(NA)
  } else {
    sentiment <- sentiment(text)
    return(mean(sentiment$sentiment))
  }
}

# parallel processing
num_cores <- detectCores() - 1 
plan(multisession, workers = num_cores)

# Apply the function to each review column
columns_to_analyze <- c("TitleReview_imdb", "FeatureReview_imdb", "top_critic_review_1_rt", "top_critic_review_2_rt", "audience_review_1_rt", "audience_review_2_rt")

# Apply sentiment analysis
for (col in columns_to_analyze) {
  sentiment_col_name <- paste0(col, "_sentiment")
  data[[sentiment_col_name]] <- future_sapply(data[[col]], get_sentiment)
}

# Shut down the parallel backend
plan(sequential)

```

Now we are going to use the average to create the overall sentiment score for the reviews of the each movie.

```{r}
# Calculate the overall sentiment score as the mean of all sentiment scores
data <- data %>%
  rowwise() %>%
  mutate(overall_sentiment_score = mean(c_across(ends_with("_sentiment")), na.rm = TRUE)) %>%
  ungroup()


remove <- c("TitleReview_imdb", "FeatureReview_imdb", "top_critic_review_1_rt", "top_critic_review_2_rt", "audience_review_1_rt", "audience_review_2_rt")


data <- data %>%
  select(-all_of(remove))
```

Merge everything and check

```{r}
data_final_5 <- merge(data_final_5, data, by = "imdb_id", all.x = TRUE)


```

## Starting with the modeling

```{r}
selected_columns <- c(
  "world_wide_gross",                
  "Budget",                                    
  "view_count_normalized",           
  "Genre_imdb.Action",               
  "Genre_imdb.Adventure",            
  "Genre_imdb.Animation",            
  "Genre_imdb.Biography",            
  "Genre_imdb.Comedy",               
  "Genre_imdb.Crime",                
  "Genre_imdb.Drama",                
  "Genre_imdb.Horror",               
  "MPAA.General Audiences",          
  "MPAA.Parental Guidance Suggested",
  "MPAA.Parents Strongly Cautioned", 
  "MPAA.Restricted",               
  "duration_normalized",             
  "release_month",                   
  "movie_age",                       
  "is_weekend",                      
  "seasonFall",                      
  "seasonSpring",                    
  "seasonSummer",                    
  "seasonWinter",                    
  "movie_score",                     
  "normalized_director_score",       
  "FirstActor_score",                
  "SecondActor_score",
  "overall_sentiment_score"
)

# Selecting the specified columns
data_final_5 <- data_final_5 %>%
  select(all_of(selected_columns))
```



**Release Month**

```{r}

data_final_5 <- data_final_5 %>% mutate(release_month = as.factor(release_month))

release_month_dummies <- model.matrix(~ release_month - 1, data = data_final_5)

release_month_dummies <- as.data.frame(release_month_dummies)
colnames(release_month_dummies) <- gsub("release_month", "month_", colnames(release_month_dummies))

data_final_5 <- cbind(data_final_5, release_month_dummies)

```

**Release Year and Age Movie**

We are going to standardize age and remove release year.

```{r}
# Normalization function
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))
}

# Normalize the movie_age variable
data_final_5$movie_age <- as.numeric(data_final_5$movie_age)
data_final_5$movie_age_scaled <- normalize(data_final_5$movie_age)

```

```{r}
data_final_5 <- data_final_5 %>%
  select(-movie_age,-release_month)
```

#### Dependent Variable

We will use the methodology used by Rhee and Zulkernine (2016) for calculating profit. Reference: Rhee, T. G., & Zulkernine, F. (2016, December). Predicting movie box office profitability: a neural network approach.

```{r}
data_final_5$Profit <- data_final_5$world_wide_gross * 0.5 - data_final_5$Budget
```

```{r}
data_final_5$Profit <- as.numeric(data_final_5$Profit)
data_final_5$Profit <- normalize(data_final_5$Profit) # normalizing profit
```

```{r}
data_final_5 <- data_final_5 %>%
  select(-Budget, -world_wide_gross)
```

```{r}
data_final_5 <- na.omit(data_final_5)
```

#### Dummy Variables

We are going to exclude one dummy variable from all our dummies to not fall into the dummy trap

```{r}
data <- data_final_5 %>%
    select(-`MPAA.Parental Guidance Suggested`,-Genre_imdb.Action)
```

### Correlation

```{r}
cor_matrix <- cor(data)
```

```{r}
fit <- lm(Profit ~ ., data = data)
summary(fit)
```
```{r}
data <- data %>%
  select(- seasonSummer,-month_5,-month_8,-month_11,-month_12 )
```


## Modeling

```{r}
set.seed(123) 
train_index <- createDataPartition(data$Profit, p = 0.8, list = FALSE)

train_set <- data[train_index, ]
test_set <- data[-train_index, ]

```

```{r}
set.seed(123)

cl <- makeCluster(detectCores() - 1)
registerDoParallel(cl)

ctrl_tune <- trainControl(method = "repeatedcv", 
                          number = 3, repeats = 1,
                          allowParallel = TRUE, 
                          returnResamp = "all", 
                          savePredictions = "all")
```

Tune Grid

```{r}
tune_grid <- expand.grid(
  C = c(0.1, 1, 5, 10, 20, 50),   
  sigma = c(0.01, 0.05, 0.1, 0.2, 0.5, 1)
)

```

Training the model

```{r}
tuned_svm_model <- train(Profit ~ ., 
                         data = train_set,
                         method = "svmRadial",
                         trControl = ctrl_tune,
                         tuneGrid = tune_grid,
                         metric = "Rsquared")

stopCluster(cl)
registerDoSEQ()
```

Visualizing results

```{r}
print(tuned_svm_model$results)

print(tuned_svm_model$resample)
```

Best Model

```{r}
best_svm_model <- tuned_svm_model$bestTune
print(best_svm_model)
```


Variable Interpretation
```{r}
var_imp_selected <- varImp(tuned_svm_model, scale = FALSE)

var_imp_selected_df <- as.data.frame(var_imp_selected$importance)
var_imp_selected_df$Variable <- rownames(var_imp_selected_df)
var_imp_selected_df <- var_imp_selected_df[order(-var_imp_selected_df$Overall), ]

top_var_imp_selected_df <- var_imp_selected_df[1:15, ]

top_var_imp_selected_df <- top_var_imp_selected_df %>%
  mutate(Variable = case_when(
    Variable == "Genre_imdb.Animation" ~ "genre_animation",
    Variable == "Genre_imdb.Crime" ~ "genre_crime",
    Variable == "MPAA.General Audiences" ~ "MPAA_general_audiences",
    Variable == "MPAA.Parents Strongly Cautioned" ~ "MPAA_parents_strongly_cautioned",
    Variable == "movie_age_scaled" ~ "movie_age",
    Variable == "view_count_normalized" ~ "view_count_trailer",
    Variable == "duration_normalized" ~ "duration_movie",
    Variable == "FirstActor_score" ~ "first_actor_star_power",
    Variable == "overall_sentiment_score" ~ "overall_sentiment_reviews",
    Variable == "normalized_director_score" ~ "director_star_power",
  Variable == "movie_score" ~ "movie_rating",



    TRUE ~ Variable
  ))

ggplot(top_var_imp_selected_df, aes(x = reorder(Variable, Overall), y = Overall, color = Overall, group = 1)) +
    geom_point(size = 3) +
    geom_segment(aes(x = reorder(Variable, Overall), 
                     xend = reorder(Variable, Overall), 
                     y = 0, 
                     yend = Overall)) +
    coord_flip() +
    labs(title = "Top 15 most important variables",
         x = NULL,
         y = "Importance") +
    scale_color_gradient(low = "#7fcdbb", high = "#253494", guide = "none") +
    theme_minimal() +
    theme(text = element_text(family = "Times New Roman", size = 11))
```

#### Prediction

To test the model in unseen data and validate the results attained

```{r}
test_set$svm_predictions <- predict(tuned_svm_model, newdata = test_set)

results_svm<- postResample(pred = test_set$svm_predictions, obs = test_set$Profit)
print(results_svm)

```

```{r}
ggplot(test_set, aes(x = svm_predictions, y = Profit)) +
  geom_point(aes(color = Profit), size = 3) +
  geom_abline(intercept = 0, slope = 1, colour = "black") +
  labs(title = "Support Vector Machine Observed vs Predicted", x = "Predicted", y = "Observed") +
  scale_color_gradient(low = "#7fcdbb", high = "#253494", guide = "none") +
  theme_minimal() +
  theme(text = element_text(family = "Times New Roman", size = 11),
        plot.title = element_text(hjust = 0.5))

```
```{r}
# SVM Model Performance
svm_predictions <- predict(tuned_svm_model, newdata = test_set)
actuals <- test_set$Profit

mse_svm <- mean((svm_predictions - actuals)^2)
rmse_svm <- sqrt(mse_svm)
mae_svm <- mean(abs(svm_predictions - actuals))
r2_svm <- 1 - sum((svm_predictions - actuals)^2) / sum((actuals - mean(actuals))^2)

cat("SVM Model Performance:\n")
cat("Mean Squared Error (MSE):", mse_svm, "\n")
cat("Root Mean Squared Error (RMSE):", rmse_svm, "\n")
cat("Mean Absolute Error (MAE):", mae_svm, "\n")
cat("R-squared (R2):", r2_svm, "\n")
```
The model has too little data, it its not good at predicting the dependent variable, the R square explains little of the variability of our dependent variable.
