---
title: "Creating the variables Part 6"
author: "Sofia Villamil"
date: "2024-06-12"
output: html_document
---

## Creating the last variables

```{r}
rm(list = ls())
```

Libraries

```{r message=FALSE}
library(sentimentr) # for the sentiment analysis
library(readr)
library(dplyr)
library(tidyverse)
library(stringr)
library(parallel)
library(future.apply)
library(scales)
library(readxl)

```

```{r message=FALSE}
data_final_6 <- read_csv("C:/Users/sofia/Documents/Documentos/Master Computational Social Sciences/TFM/Master Thesis/Modeling Part 3/data_final_6.csv",show_col_types = FALSE)
data_final_6 <- data_final_6[, -1]
```

### Actor

```{r message=FALSE}
actors_info <- read_delim("C:/Users/sofia/Documents/Documentos/Master Computational Social Sciences/TFM/Master Thesis/Modeling Part 3/actors_with_imdb.csv", 
    delim = ",", escape_double = FALSE, trim_ws = TRUE)
```

Let's start with cleaning the variable for the Oscars.

```{r}
oscar_summary <- actors_info %>%
  filter(oscars_nominations != 'Awards') %>%
  group_by(oscars_nominations) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

```

The top awards will be given waits based on this list (Link:<https://www.therichest.com/luxury/top-10-most-prestigious-movie-awards-in-the-world/>)

```{r}
award_weights <- c(
  'Won 1 Oscar' = 50,
  'Won 2 Oscars' = 100,
  'Won 3 Oscars' = 150,
  'Won 4 Oscars' = 200,
  'Won 5 Oscars' = 250,
  'Won 6 Oscars' = 300,
  'Won 1 BAFTA Award' = 30,
  'Won 2 BAFTA Awards' = 60,
  'Won 3 BAFTA Awards' = 90,  # New
  'Won 1 Primetime Emmy' = 20,
  'Won 2 Primetime Emmys' = 40,
  'Won 3 Primetime Emmys' = 60,  # New
  'Won 4 Primetime Emmys' = 80,  # New
  'Won 5 Primetime Emmys' = 100,  # New
  'Won 6 Primetime Emmys' = 120,  # New
  'Won 7 Primetime Emmys' = 140,  # New
  'Won 9 Primetime Emmys' = 180,  # New
  'Won 11 Primetime Emmys' = 220,  # New
  'Won 12 Primetime Emmys' = 240,  # New
  'Nominated for 1 Oscar' = 15,
  'Nominated for 2 Oscars' = 30,
  'Nominated for 3 Oscars' = 45,
  'Nominated for 4 Oscars' = 60,
  'Nominated for 5 Oscars' = 75,
  'Nominated for 6 Oscars' = 90,  # New
  'Nominated for 8 Oscars' = 120,  # New
  'Nominated for 12 Oscars' = 180,  # New
  'Nominated for 1 BAFTA Award' = 10,
  'Nominated for 2 BAFTA Awards' = 20,
  'Nominated for 3 BAFTA Awards' = 30,
  'Nominated for 4 BAFTA Awards' = 40,  # New
  'Nominated for 8 BAFTA Awards' = 80,  # New
  'Nominated for 1 Primetime Emmy' = 5,
  'Nominated for 2 Primetime Emmys' = 10,
  'Nominated for 3 Primetime Emmys' = 15,
  'Nominated for 4 Primetime Emmys' = 20,  # New
  'Nominated for 5 Primetime Emmys' = 25,  # New
  'Nominated for 6 Primetime Emmys' = 30,  # New
  'Nominated for 7 Primetime Emmys' = 35,  # New
  'Nominated for 8 Primetime Emmys' = 40,  # New
  'Nominated for 9 Primetime Emmys' = 45,  # New
  'Nominated for 10 Primetime Emmys' = 50,  # New
  'Nominated for 13 Primetime Emmys' = 65  # New
)

```

```{r}
actors_info <- actors_info %>%
  mutate(oscars_nominations = ifelse(oscars_nominations == "Awards", "No Major Awards", oscars_nominations))

```

Now we will clean the Awards and nomination variables

```{r}
unique_awards_nominations2 <- actors_info %>%
  select(awards_and_nominations) %>%
  distinct() %>%
  arrange(awards_and_nominations)
```

Cleaning the column as the movies with no awards need to be cleaned to represent that.

```{r}
actors_info <- actors_info %>%
  mutate(
    awards_and_nominations = ifelse(str_detect(awards_and_nominations, "win|wins|nomination|nominations"), 
                                       awards_and_nominations, 
                                       "No Awards")
  )

```

```{r}
actors_info <- actors_info %>%
  mutate(
    wins = ifelse(awards_and_nominations != "No Awards", 
                  as.numeric(str_extract(awards_and_nominations, "\\d+(?=\\s+win|\\s+wins)")), 0),
    nominations = ifelse(awards_and_nominations != "No Awards", 
                         as.numeric(str_extract(awards_and_nominations, "\\d+(?=\\s+nomination|\\s+nominations)")), 0)
  ) %>% 
  replace_na(list(wins = 0, nominations = 0))

```

For the number of movies, we need to deal first with any Na's found in that variable

```{r}
# Identify actors with NA in number_of_movies
na_actors <- actors_info %>%
  filter(is.na(number_of_movies)) %>%
  pull(name)

# Count their appearances in data_final to fill this Na's with that
actor_appearances <- data_final_6 %>%
  mutate(
    FirstActor_imdb = ifelse(FirstActor_imdb %in% na_actors, FirstActor_imdb, NA),
    SecondActor_imdb = ifelse(SecondActor_imdb %in% na_actors, SecondActor_imdb, NA)
  ) %>%
  pivot_longer(cols = c(FirstActor_imdb, SecondActor_imdb), values_drop_na = TRUE) %>%
  group_by(value) %>%
  summarize(appearances = n())

print(actor_appearances) # lets see the number of movies they appear in
```

So they each appear 1 time in our data set and in IMDb they also have only 1 previous movie so we are going to set the Na's to 1.

```{r}
actors_info <- actors_info %>%
  mutate(number_of_movies = replace_na(number_of_movies, 1))
```

Following the same calculations we did with director

```{r}
# Calculate the award score for each actor based on their awards and nominations history
actors_info <- actors_info %>%
  rowwise() %>%
  mutate(award_score = ifelse(awards_and_nominations %in% names(award_weights), award_weights[awards_and_nominations], 0)) %>%
  ungroup()

# Calculate the total award score for each actor in the data set
actor_award_score <- actors_info %>%
  group_by(actor_id_imdb) %>%
  summarise(total_award_score = sum(award_score))

# Aggregate wins and nominations for each actor for movies in the data set
actor_awards_nominations <- actors_info %>%
  group_by(actor_id_imdb) %>%
  summarise(
    total_wins = sum(wins, na.rm = TRUE),
    total_nominations = sum(nominations, na.rm = TRUE)
  )

# Combine the metrics
actor_metrics <- actors_info %>%
  select(actor_id_imdb, number_of_movies) %>% #we add the number of movies the actor has being in
  distinct() %>%
  left_join(actor_award_score, by = "actor_id_imdb") %>%
  left_join(actor_awards_nominations, by = "actor_id_imdb")

# Normalize wins and nominations
actor_metrics <- actor_metrics %>%
  mutate(
    normalized_wins = total_wins / max(total_wins, na.rm = TRUE),
    normalized_nominations = total_nominations / max(total_nominations, na.rm = TRUE)
  )

# Calculate combined actor score
actor_metrics <- actor_metrics %>%
  mutate(
    combined_actor_score = number_of_movies + total_award_score + normalized_wins * 10 + normalized_nominations * 5
  )

# Normalize the combined actor score
actor_metrics <- actor_metrics %>%
  mutate(
    min_score = min(combined_actor_score, na.rm = TRUE),
    max_score = max(combined_actor_score, na.rm = TRUE),
    normalized_actor_score = (combined_actor_score - min_score) / (max_score - min_score)
  ) %>%
  select(-min_score, -max_score)

# Merge the normalized actor score back into the original actors_info
actors_info <- actors_info %>%
  left_join(actor_metrics, by = "actor_id_imdb")

```

```{r}
columns_to_remove <- c("wins", "nominations", "award_score", "number_of_movies.y","number_of_movies.x", "total_award_score", 
                       "total_wins", "total_nominations", "normalized_wins", "normalized_nominations", 
                       "combined_actor_score", "awards_and_nominations", "oscars_nominations")


actors_info <- actors_info %>%
  select(-all_of(columns_to_remove))
```

Let's now add the rating to the final data set

```{r}
actors <- actors_info %>%
  select(-c(imdb_id,actor_id_imdb))
```

```{r}
# Merge normalized_actor_score for First Actor
data_final_6 <- data_final_6 %>%
  left_join(actors, by = c("FirstActor_imdb" = "name")) %>%
  rename(FirstActor_score = normalized_actor_score)

# Merge normalized_actor_score for Second Actor
data_final_6 <- data_final_6 %>%
  left_join(actors, by = c("SecondActor_imdb" = "name")) %>%
  rename(SecondActor_score = normalized_actor_score)
```

### Sentiment Analysis of Reviews

Let´s start with the Reviews Variable.

-   TitleReview_imdb

-   FeatureReview_imdb

-   top_critic_review_1_rt

-   top_critic_review_2_rt

-   audience_review_1_rt

-   audience_review_2_rt

```{r}
data <- data_final_6 %>%
  select(imdb_id, TitleReview_imdb, FeatureReview_imdb, top_critic_review_1_rt, top_critic_review_2_rt, audience_review_1_rt, audience_review_2_rt)

```

```{r}
# Function to calculate sentiment score using sentimentr
get_sentiment <- function(text) {
  if (is.na(text) || length(text) == 0 || text == "") {
    return(NA)
  } else {
    sentiment <- sentiment(text)
    return(mean(sentiment$sentiment))
  }
}

# parallel processing
num_cores <- detectCores() - 1 
plan(multisession, workers = num_cores)

# Apply the function to each review column
columns_to_analyze <- c("TitleReview_imdb", "FeatureReview_imdb", "top_critic_review_1_rt", "top_critic_review_2_rt", "audience_review_1_rt", "audience_review_2_rt")

# Apply sentiment analysis
for (col in columns_to_analyze) {
  sentiment_col_name <- paste0(col, "_sentiment")
  data[[sentiment_col_name]] <- future_sapply(data[[col]], get_sentiment)
}

# Shut down the parallel backend
plan(sequential)

```

Just in case. Let's check that the analysis is done correctly using the title and the review of IMDb.

```{r}
# Select specific columns I want to check
data_check <- data %>%
  select(imdb_id, TitleReview_imdb, FeatureReview_imdb)

data_check <- data_check %>%
  mutate(TitleReview_imdb_sentiment = map_dbl(TitleReview_imdb, get_sentiment),
         FeatureReview_imdb_sentiment = map_dbl(FeatureReview_imdb, get_sentiment))

# Function to classify sentiment
classify_sentiment <- function(score) {
  if (is.na(score)) {
    return("Neutral")
  } else if (score > 0.2) {
    return("Positive")
  } else if (score < -0.2) {
    return("Negative")
  } else {
    return("Neutral")
  }
}

# Classify the sentiment scores
data_check <- data_check %>%
  mutate(TitleReview_imdb_class = sapply(TitleReview_imdb_sentiment, classify_sentiment),
         FeatureReview_imdb_class = sapply(FeatureReview_imdb_sentiment, classify_sentiment))

# Check if the sentiment alignment is correct
data_check <- data_check %>%
  mutate(sentiment_alignment = case_when(
    TitleReview_imdb_class == FeatureReview_imdb_class ~ "Aligned",
    TitleReview_imdb_class == "Neutral" | FeatureReview_imdb_class == "Neutral" ~ "Aligned",
    TRUE ~ "Not Aligned"
  ))


```

Now we are going to use the average to create the overall sentiment score for the reviews of the each movie.

```{r}
# Calculate the overall sentiment score as the mean of all sentiment scores
data <- data %>%
  rowwise() %>%
  mutate(overall_sentiment_score = mean(c_across(ends_with("_sentiment")), na.rm = TRUE)) %>%
  ungroup()

# Classify the overall sentiment score to observe better the results
data <- data %>%
  mutate(overall_sentiment_class = map_chr(overall_sentiment_score, classify_sentiment))

remove <- c("TitleReview_imdb", "FeatureReview_imdb", "top_critic_review_1_rt", "top_critic_review_2_rt", "audience_review_1_rt", "audience_review_2_rt")


data <- data %>%
  select(-all_of(remove))
```

Merge everything and check

```{r}
data_final_6 <- merge(data_final_6, data, by = "imdb_id", all.x = TRUE)

data_final_dd <- data_final_6 %>% select(title, overall_sentiment_class, overall_sentiment_score, TitleReview_imdb, FeatureReview_imdb, top_critic_review_1_rt, top_critic_review_2_rt, audience_review_1_rt, audience_review_2_rt)

```

```{r}
#write.csv(data_final_6, "C:/Users/sofia/Documents/Documentos/Master Computational Social Sciences/TFM/Master Thesis/Modeling Final Part 4/data_final_7.csv", row.names = FALSE)
```

Now we continue to the script called Model_Part_2
