---
title: "Creation of the variables"
author: "Sofia Villamil"
date: "2024-06-10"
output: html_document
---

```{r}
rm(list = ls())
```

#### Libraries

```{r}
library(readr)
library(caret)
library(tidyverse)
library(sentimentr) # for the sentiment analysis
library(lubridate) # for release data
```

```{r}
data_final <- read_csv("C:/Users/sofia/Documents/Documentos/Master Computational Social Sciences/TFM/Master Thesis/Scrapping and Data Part 2/data_final_5.csv", show_col_types = FALSE)
```

### Sentiment Analysis of Reviews

Let´s start with the Reviews Variable.

-   TitleReview_imdb

-   FeatureReview_imdb

-   top_critic_review_1_rt

-   top_critic_review_2_rt

-   audience_review_1_rt

-   audience_review_2_rt

```{r}
data <- data_final %>%
  select(imdb_id, TitleReview_imdb, FeatureReview_imdb, top_critic_review_1_rt, top_critic_review_2_rt, audience_review_1_rt, audience_review_2_rt)

```

```{r}
# Function to calculate sentiment score using sentimentr
get_sentiment <- function(text) {
  if (is.na(text) || length(text) == 0) {
    return(NA)
  } else {
    sentiment <- sentiment(text)
    return(mean(sentiment$sentiment))
  }
}

# Apply the function to each review column, excluding 'imdb_id'
data <- data %>%
  mutate(across(c(TitleReview_imdb, FeatureReview_imdb, top_critic_review_1_rt, top_critic_review_2_rt, audience_review_1_rt, audience_review_2_rt), 
                ~ map_dbl(.x, get_sentiment), .names = "{col}_sentiment"))

```

Let's check that the analysis is done correctly using the title and the review of imdb.

```{r}
# Select specific columns and store them in a new tibble
data_check <- data_final %>%
  select(imdb_id, TitleReview_imdb, FeatureReview_imdb)


# Apply the function to the TitleReview_imdb and FeatureReview_imdb columns
data_check <- data_check %>%
  mutate(TitleReview_imdb_sentiment = map_dbl(TitleReview_imdb, get_sentiment),
         FeatureReview_imdb_sentiment = map_dbl(FeatureReview_imdb, get_sentiment))

# Function to classify sentiment
classify_sentiment <- function(score) {
  if (is.na(score)) {
    return("Neutral")
  } else if (score > 0.2) {
    return("Positive")
  } else if (score < -0.2) {
    return("Negative")
  } else {
    return("Neutral")
  }
}

# Classify the sentiment scores
data_check <- data_check %>%
  mutate(TitleReview_imdb_class = sapply(TitleReview_imdb_sentiment, classify_sentiment),
         FeatureReview_imdb_class = sapply(FeatureReview_imdb_sentiment, classify_sentiment))

# Check if the sentiment alignment is correct
data_check <- data_check %>%
  mutate(sentiment_alignment = case_when(
    TitleReview_imdb_class == FeatureReview_imdb_class ~ "Aligned",
    TitleReview_imdb_class == "Neutral" | FeatureReview_imdb_class == "Neutral" ~ "Aligned",
    TRUE ~ "Not Aligned"
  ))

# Display the result
print(data_check)

```

Now we are going to use the average to create the overall sentiment score for the reviews of the each movie.

```{r}
# Calculate the overall sentiment score as the mean of all sentiment scores
data <- data %>%
  rowwise() %>%
  mutate(overall_sentiment_score = mean(c_across(ends_with("_sentiment")), na.rm = TRUE)) %>%
  ungroup()

# Display the result
print(data)

```

### Genre

```{r}
unique_genres <- data_final %>%
  group_by(Genre_imdb) %>%
  summarise(count = n()) %>%
  ungroup()
```

Checked individually the most unique genres and look into the titles

```{r}
unique_genres <- data_final %>%
  select(title, Genre_imdb) %>%
  filter(Genre_imdb == "Romance")
unique_genres
```

We are going to reduce the types of genre to the main one by using Rotten Tomatoes genres

```{r}
# Update the genre for the movie
data_final <- data_final %>%
  mutate(Genre_imdb = case_when(
    title == "Bennett's War" ~ "Drama",
    title == "Sympathy for the Devil" ~ "Thriller",
    title == "D-Day Assassins" ~ "Drama",
    title == "Nefta Football Club" ~ "Comedy",
    title == "The Neighbors' Window" ~ "Drama",
    title == "The Staggering Girl" ~ "Drama",
    title == "Strange Way of Life" ~ "Romance",
    Genre_imdb == "History" ~ "Drama",
    TRUE ~ Genre_imdb
  ))

```

Creating the genre dummy for analysis, it will take the value one if the movie is a certain genre.

```{r}
# Ensure Genre_imdb is a factor
data_final <- data_final %>%
  mutate(Genre_imdb = factor(Genre_imdb))

# crating the dummy variables
dummy <- dummyVars(" ~ Genre_imdb", data = data_final)
data_final_encoded <- as.data.frame(predict(dummy, newdata = data_final))

```

```{r}
# combining the columns
data_final <- bind_cols(data_final, data_final_encoded)

data_final <- data_final %>%
  select(-Genre_imdb)
```

### MPAA

```{r}
unique_MPAA <- data_final %>%
  group_by(MPAA_imdb) %>%
  summarise(count = n()) %>%
  ungroup()
unique_MPAA
```

There are 36 distinct ratings, we will standardize it for the analysis using the Motion Pictures Association Rating Guide (Click here for the interactive guide: <https://www.motionpictures.org/film-ratings/>).

```{r}
# Function to standardize ratings
standardize_rating <- function(rating) {
  case_when(
    rating %in% c("G", "TV-Y", "TV-G", "A", "AL", "TP", "A/fig", "A/i", "A/i/fig", "0+", "3", "4", "6+", "TV-Y7") ~ "General Audiences",
    rating %in% c("PG", "TV-PG", "2", "5", "7","7/i","7/fig","10", "12", "12/fig", "13", "13+") ~ "Parental Guidance Suggested",
    rating %in% c("PG-13", "TV-14", "14", "16", "16+", "16/fig", "9+", "M") ~ "Parents Strongly Cautioned",
    rating %in% c("R", "TV-MA", "18", "18+", "18/fig", "NC-17", "X") ~ "Restricted",
    rating %in% c("NC-17") ~ "No One 17 and Under Admitted",
    rating %in% c("Not Rated") ~ "Not Rated",
    TRUE ~ "Unknown"
  )
}

# Apply the function to standardize ratings
data_final <- data_final %>%
  mutate(MPAA = standardize_rating(MPAA_imdb))

# transforming it as a factor
data_final <- data_final %>%
  mutate(MPAA = factor(MPAA))

# Check if there are categories that are "Unknown"
unknown_values <- data_final %>%
  filter(MPAA == "Unknown") %>%
  select(MPAA_imdb) %>%
  distinct() 
# there are no unknown values!
```

```{r}
# Creating the dummy variable
dummy_mpaa <- dummyVars(" ~ MPAA", data = data_final)
data_final_encoded_mpaa <- as.data.frame(predict(dummy_mpaa, newdata = data_final))

data_final <- bind_cols(data_final, data_final_encoded_mpaa)

data_final <- data_final %>%
  select(-MPAA_imdb, -MPAA)
```

### Original Language

```{r}
unique_Lang <- data_final %>%
  select(original_language) %>%
  distinct()
unique_Lang
```

```{r}
data_final <- data_final %>%
  mutate(original_language= factor(original_language))

dummy_lang <- dummyVars(" ~ original_language", data = data_final)
data_final_encoded_lang <- as.data.frame(predict(dummy_lang, newdata = data_final))

data_final <- bind_cols(data_final, data_final_encoded_lang)

data_final <- data_final %>%
  select(-original_language)
```

### Duration of the movie

```{r}
# Normalize the duration variable between 0 and 1
data_final <- data_final %>%
  mutate(duration_normalized = (Duration_mov_imdb- min(Duration_mov_imdb)) / (max(Duration_mov_imdb) - min(Duration_mov_imdb)))

summary(data_final$duration_normalized)
data_final <- data_final %>%
  select(-Duration_mov_imdb)
```

### Release Date

```{r}
data_final <- data_final %>%
  mutate(release_date = dmy(release_date))
```

```{r}
# Extract year, month, and day
data_final <- data_final %>%
  mutate(release_year = year(release_date),
         release_month = month(release_date),
         release_day = day(release_date))

# Calculate the age of the movie
current_year <- year(Sys.Date())
data_final <- data_final %>%
  mutate(movie_age = current_year - release_year)

# Create a feature to determine if the release date is a weekend
data_final <- data_final %>%
  mutate(is_weekend = if_else(wday(release_date) %in% c(1, 7), 1, 0))

```

Season

```{r}
# Create a feature for the season 
data_final <- data_final %>%
  mutate(season = case_when(
    month(release_date) %in% c(12, 1, 2) ~ "Winter",
    month(release_date) %in% c(3, 4, 5) ~ "Spring",
    month(release_date) %in% c(6, 7, 8) ~ "Summer",
    month(release_date) %in% c(9, 10, 11) ~ "Fall"
  ))

```

```{r}
# Creating a dummy variable
data_final <- data_final %>%
  mutate(season_ = factor(season))

dummy_season <- dummyVars(" ~ season", data = data_final)
data_final_encoded_season <- as.data.frame(predict(dummy_season, newdata = data_final))

data_final <- bind_cols(data_final, data_final_encoded_season)

data_final <- data_final %>%
  select(-release_date, -season)
```

### Budget

There are a lot of NA's in budget and I believe that imputing will affect the final results, so I have decided to eliminate this variable.

data_final \<- data_final %\>%

select(-Budget)

```{r}
na_count <- sum(is.na(data_final $Budget))
na_count
```

### Production Companies

There are a lot of production companies that appear 1 time in the data set. This is not going to bring little to no insight into the analysis as we do not have enough observations for each so I have decided to eliminate it.

```{r}
unique_prod <- data_final %>%
  group_by(production_companies) %>%
  summarise(count = n()) %>%
  ungroup()
unique_prod

```

```{r}
data_final <- data_final %>%
  select(-production_companies)
```

### World Wide Gross (Dependent Variables)

```{r}
# Visualize the distribution with a histogram
ggplot(data_final, aes(x = world_wide_gross)) +
  geom_histogram(binwidth = 5000000000, fill = "blue", color = "black", alpha = 0.7) +
  labs(title = "Distribution of World Wide Gross", x = "World Wide Gross", y = "Frequency")

# Visualize the distribution with a density plot
ggplot(data_final, aes(x = world_wide_gross)) +
  geom_density(fill = "blue", alpha = 0.7) +
  labs(title = "Density Plot of World Wide Gross", x = "World Wide Gross", y = "Density")

# Visualize the distribution with a boxplot
ggplot(data_final, aes(y = world_wide_gross)) +
  geom_boxplot(fill = "blue", alpha = 0.7) +
  labs(title = "Boxplot of World Wide Gross", y = "World Wide Gross")

# Summary statistics
summary_stats <- data_final %>%
  summarise(
    mean = mean(world_wide_gross, na.rm = TRUE),
    median = median(world_wide_gross, na.rm = TRUE),
    sd = sd(world_wide_gross, na.rm = TRUE),
    min = min(world_wide_gross, na.rm = TRUE),
    max = max(world_wide_gross, na.rm = TRUE)
  )

print(summary_stats)

```

```{r}
# Calculate the 90th and 95th percentile as potential thresholds for success
threshold_90 <- quantile(data_final$world_wide_gross, 0.90, na.rm = TRUE)

print(threshold_90)

# Choose the 90th percentile as the success threshold for this example
success_threshold <- threshold_90

# Create binary target variable for success
data_final <- data_final %>%
  mutate(success = if_else(world_wide_gross >= success_threshold, 1, 0))

```

```{r}
# Select the title and success columns
selected_data <- data_final %>%
  select(title,Budget,success)

# View the selected columns
View(selected_data)
```
