---
title: "Creation of the variables"
author: "Sofia Villamil"
date: "2024-06-10"
output: html_document
---

## Creation of the final variables we are going to use in this analysis

```{r}
rm(list = ls())
```

#### Libraries

```{r message=FALSE}
library(readr)
library(caret)
library(tidyverse)
library(lubridate) # for release data
library(scales)
library(stringr)
library(tidyr)
```

```{r}
data_final <- read_csv("C:/Users/sofia/Documents/Documentos/Master Computational Social Sciences/TFM/Master Thesis/Scrapping and Data Part 2/data_final_5.csv", show_col_types = FALSE)

data_final <- data_final %>%
  select(-title_rt,-title_scraped,-MovieID)
```

### Budget

There are a lot of NA's in budget and I believe that imputing will affect the final results, so I have decided to eliminate this variable.

```{r}
na_count <- sum(is.na(data_final$Budget))
na_count
```

We have decided that the best course of action is to eliminate the rows with NA values in the Budget column. Due to establishing that the dependent variable will be based on the literature reviews and how the majority of the papers treat the dependent variable, we have made the decision that all the movies without a budget will not be considered. Considering our previous work on the success variable, which was created to have a sense of what could be considered a successful movie, it is essential to ensure the accuracy of our data. Ignoring the budget in our metric for the dependent variable could result in movies with negative profits being incorrectly classified as successes with what we could observed happen with that variable.

```{r}
data_final<- data_final %>%
  filter(!is.na(Budget))
```

### Genre

```{r}
unique_genres <- data_final %>%
  group_by(Genre_imdb) %>%
  summarise(count = n()) %>%
  ungroup()
```

Checked individually the most unique genres and look into the titles

```{r}
unique_genres2 <- data_final %>%
  select(title, Genre_imdb) %>%
  filter(Genre_imdb == "Sci-Fi")
```

We are going to reduce the types of genre to the main one by using Rotten Tomatoes genres also

```{r}
# Update the genre for the movie
data_final <- data_final %>%
  mutate(Genre_imdb = case_when(
    title == "The Boy Next Door" ~ "Mystery",
    title == "The Bar" ~ "Mystery",
    title == "97 Minutes" ~ "Mystery",
    title == "A Christmas Star" ~ "Adventure",
    title == "App" ~ "Mystery",
    TRUE ~ Genre_imdb
  ))

```

The rest we eliminate.

```{r}
data_final <- data_final %>%
  group_by(Genre_imdb) %>%
  filter(n() > 1) %>%
  ungroup()
```

Creating the genre dummy for analysis, it will take the value one if the movie is a certain genre.

```{r}
# Ensure Genre is a factor
data_final <- data_final %>%
  mutate(Genre_imdb = factor(Genre_imdb))

# crating the dummy variables
dummy <- dummyVars(" ~ Genre_imdb", data = data_final)
data_final_encoded <- as.data.frame(predict(dummy, newdata = data_final))

```

```{r}
# combining the columns
data_final <- bind_cols(data_final, data_final_encoded)

data_final <- data_final %>%
  select(-Genre_imdb)
```

### MPAA

```{r}
unique_MPAA <- data_final %>%
  group_by(MPAA_imdb) %>%
  summarise(count = n()) %>%
  ungroup()
unique_MPAA
```

There are 36 distinct ratings, we will standardize it for the analysis using the Motion Pictures Association Rating Guide (Click here for the interactive guide: <https://www.motionpictures.org/film-ratings/>).

```{r}
# Function to standardize ratings
standardize_rating <- function(rating) {
  case_when(
    rating %in% c("G", "TV-Y", "TV-G", "A", "AL", "TP", "A/fig", "A/i", "A/i/fig", "0+", "3", "4", "6+", "TV-Y7") ~ "General Audiences",
    rating %in% c("PG", "TV-PG", "2", "5", "7","7/i","7/fig","10", "12", "12/fig", "13", "13+") ~ "Parental Guidance Suggested",
    rating %in% c("PG-13", "TV-14", "14", "16", "16+", "16/fig", "9+", "M") ~ "Parents Strongly Cautioned",
    rating %in% c("R", "TV-MA", "18", "18+", "18/fig", "NC-17", "X") ~ "Restricted",
    rating %in% c("NC-17") ~ "No One 17 and Under Admitted",
    rating %in% c("Not Rated") ~ "Not Rated",
    TRUE ~ "Unknown"
  )
}

# Apply the function to standardize ratings
data_final <- data_final %>%
  mutate(MPAA = standardize_rating(MPAA_imdb))

# transforming it as a factor
data_final <- data_final %>%
  mutate(MPAA = factor(MPAA))

# Check if there are categories that are "Unknown"
unknown_values <- data_final %>%
  filter(MPAA == "Unknown") %>%
  select(MPAA_imdb) %>%
  distinct() 
# there are no unknown values!
```

```{r}
# Creating the dummy variable
dummy_mpaa <- dummyVars(" ~ MPAA", data = data_final)
data_final_encoded_mpaa <- as.data.frame(predict(dummy_mpaa, newdata = data_final))

data_final <- bind_cols(data_final, data_final_encoded_mpaa)

data_final <- data_final %>%
  select(-MPAA_imdb, -MPAA)
```

### Original Language

```{r}
data_final <- data_final %>%
  select(-original_language)
```

There are to little observations for each language some even have none observations.

### Duration of the movie

```{r}
# Normalize the duration variable between 0 and 1
data_final <- data_final %>%
  mutate(duration_normalized = (Duration_mov_imdb- min(Duration_mov_imdb)) / (max(Duration_mov_imdb) - min(Duration_mov_imdb)))

summary(data_final$duration_normalized)
data_final <- data_final %>%
  select(-Duration_mov_imdb)
```

### Release Date

```{r}
data_final <- data_final %>%
  mutate(release_date = dmy(release_date))
```

```{r}
# Extract year, month, and day
data_final <- data_final %>%
  mutate(release_year = year(release_date),
         release_month = month(release_date),
         release_day = day(release_date))

# Calculate the age of the movie
current_year <- year(Sys.Date())
data_final <- data_final %>%
  mutate(movie_age = current_year - release_year)

# Create a feature to determine if the release date is a weekend
data_final <- data_final %>%
  mutate(is_weekend = if_else(wday(release_date) %in% c(1, 7), 1, 0))

```

Season

```{r}
data_final <- data_final %>%
  mutate(season = case_when(
    month(release_date) %in% c(12, 1, 2) ~ "Winter",
    month(release_date) %in% c(3, 4, 5) ~ "Spring",
    month(release_date) %in% c(6, 7, 8) ~ "Summer",
    month(release_date) %in% c(9, 10, 11) ~ "Fall"
  ))

```

```{r}
# Creating a dummy variable
data_final <- data_final %>%
  mutate(season_ = factor(season))

dummy_season <- dummyVars(" ~ season", data = data_final)
data_final_encoded_season <- as.data.frame(predict(dummy_season, newdata = data_final))

data_final <- bind_cols(data_final, data_final_encoded_season)

data_final <- data_final %>%
  select(-release_date, -season_)
```

### Production Companies

There are a lot of production companies that appear 1 time in the data set. This is not going to bring little to no insight into the analysis as we do not have enough observations for each so I have decided to eliminate it.

```{r}
unique_prod <- data_final %>%
  group_by(production_companies) %>%
  summarise(count = n()) %>%
  ungroup()
unique_prod

```

```{r}
data_final <- data_final %>%
  select(-production_companies)
```

### World Wide Gross (Dependent Variables)

```{r}
# Visualize the distribution with a boxplot
ggplot(data_final, aes(y = world_wide_gross)) +
  geom_boxplot(fill = "blue", alpha = 0.7) +
  labs(title = "Boxplot of World Wide Gross", y = "World Wide Gross")

# Summary statistics
summary_stats <- data_final %>%
  summarise(
    mean = mean(world_wide_gross, na.rm = TRUE),
    median = median(world_wide_gross, na.rm = TRUE),
    sd = sd(world_wide_gross, na.rm = TRUE),
    min = min(world_wide_gross, na.rm = TRUE),
    max = max(world_wide_gross, na.rm = TRUE)
  )

print(summary_stats)

```

```{r}
# Calculate the 90th and 95th percentile as potential thresholds for success
threshold_90 <- quantile(data_final$world_wide_gross, 0.90, na.rm = TRUE)

print(threshold_90)

# Choose the 90th percentile as the success threshold for this example
success_threshold <- threshold_90

# Create binary target variable for success
data_final <- data_final %>%
  mutate(success = if_else(world_wide_gross >= success_threshold, 1, 0))

```

```{r}
# Select relevant columns and create new ones
selected_data2 <- data_final %>%
  select(title, Budget, world_wide_gross, success) %>%
  mutate(
    profit = world_wide_gross - Budget,
    marketing = 0.5 * Budget, # it said it on the literature
    new_budget = marketing + Budget,
    actual_prof = world_wide_gross - new_budget
  ) %>%
  mutate(across(c(Budget, world_wide_gross, profit, new_budget, actual_prof), comma))

```

### Score

We are going to create a combined score, using the three scores attained and the total voting for those score.

```{r}
# First we normalize IMDb scores to a 0-100 scale equal to the rt one.
data_final <- data_final %>%
  mutate(imdb_score_normalized = IMDbscore_imdb * 10)
```

I decided to do this instead of differentiating between the three because I want to concentrate the impact of this score in the revenue, not the impact that each has on the revenue of a movie.

Now, I have some missing values but I dont want to loose information that the movies with this missing values is going to give me so we are going to create a mix approach to calculate the score.

```{r}
data_final <- data_final %>%
  rowwise() %>%
  mutate(
    # cases with all scores
    weighted_sum_all = sum(
      na.omit(c(imdb_score_normalized,
                critics_score_rt * total_critics_reviews_rt,
                audience_score_rt * total_audience_reviews_rt))),
    total_reviews_all = sum(
      na.omit(c(1, total_critics_reviews_rt, total_audience_reviews_rt))),
    combined_score_all = ifelse(total_reviews_all > 0, weighted_sum_all / total_reviews_all, NA),
    
    # cases missing audience scores
    weighted_sum_no_audience = sum(
      na.omit(c(imdb_score_normalized,
                critics_score_rt * total_critics_reviews_rt))),
    total_reviews_no_audience = sum(
      na.omit(c(1, total_critics_reviews_rt))),
    combined_score_no_audience = ifelse(total_reviews_no_audience > 0, weighted_sum_no_audience / total_reviews_no_audience, NA),
    
    # cases missing critics' scores
    weighted_sum_no_critics = sum(
      na.omit(c(imdb_score_normalized,
                audience_score_rt * total_audience_reviews_rt))),
    total_reviews_no_critics = sum(
      na.omit(c(1, total_audience_reviews_rt))),
    combined_score_no_critics = ifelse(total_reviews_no_critics > 0, weighted_sum_no_critics / total_reviews_no_critics, NA),
    
    # cases with only IMDb scores
    combined_score_imdb_only = imdb_score_normalized,
    
    # combined score creation
    combined_score = case_when(
      !is.na(combined_score_all) ~ combined_score_all,
      !is.na(combined_score_no_audience) ~ combined_score_no_audience,
      !is.na(combined_score_no_critics) ~ combined_score_no_critics,
      TRUE ~ combined_score_imdb_only
    )
  ) %>%
  ungroup()
```

```{r}
data_final <- data_final %>%
  mutate(
    min_combined_score = min(combined_score, na.rm = TRUE),
    max_combined_score = max(combined_score, na.rm = TRUE),
    movie_score = (combined_score - min_combined_score) / (max_combined_score - min_combined_score)
  )
```

```{r}
data_final <- data_final %>%
  select(-min_combined_score, -max_combined_score, -IMDbscore_imdb, -imdb_score_normalized,
         -weighted_sum_all, -total_reviews_all, -combined_score_all,
         -weighted_sum_no_audience, -total_reviews_no_audience, -combined_score_no_audience,
         -weighted_sum_no_critics, -total_reviews_no_critics, -combined_score_no_critics,
         -combined_score_imdb_only, -combined_score)

```

### Director

Let's start with cleaning the variable for the Oscars.

```{r}
oscar_summary <- data_final %>%
  filter(Oscar_Information_imdb != 'Awards') %>%
  group_by(Oscar_Information_imdb) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

```

The top awards will be given waits based on this list (Link:<https://www.therichest.com/luxury/top-10-most-prestigious-movie-awards-in-the-world/>)

```{r}
award_weights <- c(
  'Won 1 Oscar' = 50,
  'Won 2 Oscars' = 100,
  'Won 3 Oscars' = 150,
  'Won 4 Oscars' = 200,
  'Won 5 Oscars' = 250,
  'Won 6 Oscars' = 300,
  'Won 7 Oscars' = 350,
  'Won 1 BAFTA Award' = 30,
  'Won 2 BAFTA Awards' = 60,
  'Won 1 Primetime Emmy' = 20,
  'Won 2 Primetime Emmys' = 40,
  'Nominated for 1 Oscar' = 15,
  'Nominated for 2 Oscars' = 30,
  'Nominated for 3 Oscars' = 45,
  'Nominated for 4 Oscars' = 60,
  'Nominated for 5 Oscars' = 75,
  'Nominated for 1 BAFTA Award' = 10,
  'Nominated for 2 BAFTA Awards' = 20,
  'Nominated for 3 BAFTA Awards' = 30,
  'Nominated for 1 Primetime Emmy' = 5,
  'Nominated for 2 Primetime Emmys' = 10,
  'Nominated for 3 Primetime Emmys' = 15
)

```

```{r}
data_final <- data_final %>%
  mutate(Oscar_Information_imdb = ifelse(Oscar_Information_imdb == "Awards", "No Major Awards", Oscar_Information_imdb))

```

Taking into account that I will also get the number of awards and nominations.

Now we will clean the Awards and nomination variables

```{r}
unique_awards_nominations <- data_final %>%
  select(AwardsAndNominations_imdb) %>%
  distinct() %>%
  arrange(AwardsAndNominations_imdb)
```

Cleaning the column as the movies with no awards need to be cleaned to represent that.

```{r}
data_final <- data_final %>%
  mutate(
    AwardsAndNominations_imdb = ifelse(str_detect(AwardsAndNominations_imdb, "win|wins|nomination|nominations"), 
                                       AwardsAndNominations_imdb, 
                                       "No Awards")
  )

```

```{r}
# Extract wins and nominations
data_final <- data_final %>%
  mutate(
    wins = ifelse(AwardsAndNominations_imdb != "No Awards", 
                  as.numeric(str_extract(AwardsAndNominations_imdb, "\\d+(?=\\s+win|\\s+wins)")), 0),
    nominations = ifelse(AwardsAndNominations_imdb != "No Awards", 
                         as.numeric(str_extract(AwardsAndNominations_imdb, "\\d+(?=\\s+nomination|\\s+nominations)")), 0)
  ) %>% 
  replace_na(list(wins = 0, nominations = 0))

```

```{r}
# Calculate the award score for each director based on their awards and nominations history in my data set
data_final <- data_final %>%
  rowwise() %>%
  mutate(award_score = ifelse(Oscar_Information_imdb %in% names(award_weights), award_weights[Oscar_Information_imdb], 0)) %>%
  ungroup()

# Calculate the number of movies each director has directed in the data set
director_movie_count <- data_final %>%
  group_by(Director_imdb) %>%
  summarise(movie_count = n())

# Calculate the total award score for each director in the data set
director_award_score <- data_final %>%
  group_by(Director_imdb) %>%
  summarise(total_award_score = sum(award_score))

# Aggregate wins and nominations for each director for movies in the data set
director_awards_nominations <- data_final %>%
  group_by(Director_imdb) %>%
  summarise(
    total_wins = sum(wins, na.rm = TRUE),
    total_nominations = sum(nominations, na.rm = TRUE)
  )

director_metrics <- director_movie_count %>%
  left_join(director_award_score, by = "Director_imdb") %>%
  left_join(director_awards_nominations, by = "Director_imdb")

# Normalize wins and nominations to ensure that many small awards don't overshadow big ones. I want the important awards to still have weight.
director_metrics <- director_metrics %>%
  mutate(
    normalized_wins = total_wins / max(total_wins, na.rm = TRUE),
    normalized_nominations = total_nominations / max(total_nominations, na.rm = TRUE)
  )

# combined director score
director_metrics <- director_metrics %>%
  mutate(
    combined_director_score = movie_count + total_award_score + normalized_wins * 10 + normalized_nominations * 5
  )

# Normalize the combined director score 
director_metrics <- director_metrics %>%
  mutate(
    min_score = min(combined_director_score, na.rm = TRUE),
    max_score = max(combined_director_score, na.rm = TRUE),
    normalized_director_score = (combined_director_score - min_score) / (max_score - min_score)
  ) %>%
  select(-min_score, -max_score)


data_final <- data_final %>%
  left_join(director_metrics, by = "Director_imdb")


```

```{r}
columns_to_remove <- c("wins", "nominations", "award_score", "movie_count", "total_award_score", 
                       "total_wins", "total_nominations", "normalized_wins", "normalized_nominations", 
                       "combined_director_score", "Oscar_Information_imdb", "AwardsAndNominations_imdb")

data_final <- data_final %>%
  select(-all_of(columns_to_remove))
```

### Gender

Let's fix the gender variable and complete the Na's.

```{r}
directors_with_missing_gender <- data_final %>%
  filter(is.na(director_is_woman)) %>%
  select(Director_imdb) %>%
  distinct()

print(directors_with_missing_gender)
```

```{r}
# List of women directors 
women_directors <- c(
  "Gaysorn Thavat", "Anca Miruna Lazarescu", "Armagan Ballantyne", "Soudade Kaadan",
  "Vesela Kazakova", "Luàna Bajrami", "Neus Ballús", "Erige Sehiri", "Amélie van Elmbt",
  "Kiruthiga Udhayanidhi", "Gunhild Magnor", "Kurdwin Ayub", "Manane Rodríguez",
  "Senem Tüzen", "Coky Giedroyc", "Kestrin Pantera", "Cláudia Varejão", "Heiward Mak",
  "Oeke Hoogendijk", "Valérie Massadian", "Feihong Chen", "Lucía Garibaldi", 
  "Anne-Lise Koehler", "Hnin Ei Hlaing", "Ramata-Toulaye Sy", "Ángeles Cruz",
  "Tizza Covi", "Becs Arahanga", "Aitch Alberto", "Naziha Arebi", "Eun-Jeong Yu",
  "Tanwarin Sukkhapisit"
)

data_final$director_is_woman <- ifelse(data_final$Director_imdb %in% women_directors, 1, 0)

data_final$director_is_woman[is.na(data_final$Director_imdb)] <- NA
```

Now for the Lead is a Woman

```{r}
actor_with_missing_gender <- data_final %>%
  filter(is.na(lead_is_woman)) %>%
  select(FirstActor_imdb) %>%
  distinct()

print(actor_with_missing_gender)
```

```{r}
women_actors <- c(
  "Chia-Yen Ko", "Elín Hall", "LisaGay Hamilton", "Gwei Lun-Mei", "Karelle Tremblay",
  "Thitiya Jirapornsilp", "Nuria Giménez", "Algi Eke", "Huifang Duan", "Jyotika",
  "Fala Chen", "Ladya Cheryl", "Gong Linna", "Kinuko Tanida", "Luàna Bajrami",
  "Bipasha Basu", "Yile Yara Vianello", "Jowita Budnik", "Moa Stefansdotter",
  "Ameni Fdhili", "Iride Mockert", "Dextina Booker", "Mbong Amata", "Suhaee Abro",
  "Amber Fares", "Delfine Bafort", "Chuan-Ying Chuang", "Youssra", "Mbissine Thérèse Diop",
  "María Fux", "Kristii Schneider", "Gerlinde Kaltenbrunner", "Lola Arias",
  "Hong-Anh", "Awatea Mita", "Jill Li", "Thishiwe Ziqubu", "Musetta Vander",
  "Preity G Zinta", "Hennika Huuse", "Freny Bhagat", "Yunjin Cao", "Shehr Ali",
  "Angdu Padma", "Woseser Tsering", "Tanaquil Le Clerq", "Fine Sendel", "Mãlina Manovici",
  "Parineeti Chopra", "Ha Le Diem", "Hnin Ei Hlaing", "Anaita Wali Zada",
  "Trien de Haan-Zwagerman", "Paca Molera Pereira", "Dada Chan", "Ro Mereani Adi Tuimatanisiga",
  "Whirimako Black", "Mía Maestro", "Shamira Raphaela", "Inês Sá Frias",
  "Gcina Mhlophe", "Crystal-Donna Roberts", "Meezaan Jafri", "Anzhelika Hakobyan",
  "Basê Dogan", "Hyomin", "Cindy Jansen", "Nisrine Amine", "Kovai Sarala",
  "Rhae-Kye Waites", "Magdaléna Borová"
)

data_final$lead_is_woman <- ifelse(data_final$FirstActor_imdb %in% women_actors, 1, 0)

data_final$lead_is_woman[is.na(data_final$FirstActor_imdb)] <- NA
```

```{r}
#write.csv(data_final, "C:/Users/sofia/Documents/Documentos/Master Computational Social Sciences/TFM/Master Thesis/Modeling Part 3/data_final_6.csv")

```

We will continue now with the variables for the actors in the next script called "Creating the variables_Part_2"
