---
title: "Creating the Variables_Part_3"
author: "Sofia Villamil"
date: "2024-06-14"
output: html_document
---
## Instagram and Youtube data set
We are going to prepare the data set for scrapping using python scripts

```{r}
rm(list = ls())
```


```{r}
library(readr)
library(openxlsx)
```


```{r message = FALSE}
data_final_6 <- read_csv("C:/Users/sofia/Documents/Documentos/Master Computational Social Sciences/TFM/Master Thesis/Modeling Part 3/data_final_6.csv", show_col_types = FALSE)

```


### Data set samples for Scrapping in Youtube with python script

```{r}
movies2 <- data_final_6 %>% select(imdb_id, title)

#write.csv(movies2, "C:/Users/sofia/Documents/Documentos/Master Computational Social Sciences/TFM/Master Thesis/Modeling Part 3/Youtube and Instagram Data/data_final_movies.csv",row.names = FALSE)

```

### Data set samples for Scrapping in Instagram with python script

```{r}
data_filtered <- read_csv("C:/Users/sofia/Documents/Documentos/Master Computational Social Sciences/TFM/Master Thesis/Modeling Part 3/actors_with_imdb.csv", show_col_types = FALSE)
```


```{r}
nombres <- data_filtered %>% select(name)

#write.xlsx(nombres, "C:/Users/sofia/Documents/Documentos/Master Computational Social Sciences/TFM/Master Thesis/Modeling Part 3/Youtube and Instagram Data/data_final_actores_full.xlsx", rowNames = FALSE)

```

We will now do the Instagram Script and the YouTube Script. They are python scripts called "Instagram_Part_4" and "Youtube_Part_5". And then we continue with the final Folder called Modeling Final Part 4

